Learning and comparing functional connectomes between populations

### 2012-12-28 paper.tex
Add missing files
iter of graph-topology appraoches

\paragraph{Graph-topology metrics}
%
Small world networks, transport properties, resilient...
\cite{achard2006,bullmore2009}

>>>>

\paragraph{Graph-topology metrics}
%
Functional connectivity graphs have been found to display specific
topological properties\footnote{In the neuroscience world, these
descriptions are group under the terms of ``graph theoretical
approaches'', however graph theory is an entire division of mathematics
and computer science that is concerned with much more than topology of
random graphs.} that are characteristic of small-word networks
\cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
display excellent transport properties: although they display relatively
small number of connections, any two regions of the brain are well
connected. Another interesting consequence of their specific topology is
the resilience it gives to the system to attacks such as resulting from
brain lesions \cite{achard2006}. This overall structure of
functional-connectivity graphs can be summarized by a few metrics, such
as the average path length between any two nodes or the local clustering
coefficients. Given that pathologies without a well-defined focus, such
as schizophrenia, are thought to have a global impact on brain
connectivity \cite{liu2008,bassett2008}, it is interesting to use the
graph-topology metrics to perform inter-subject comparison. Such an
approach is appealing as it is not subject to multiple comparison issues.
However, it has been criticized as giving a fairly unspecific
characterization of the brain and being fragile to noise 
\cite{ioannides2007}.
